Smooth risk-based predictive approaches to treatment effect heterogeneity: A simulation study

### 2021-06-09 submission/manuscript.rmd
add gusto plot
remove deviations plor and rerun manuscript creation

A true logistic regression model with a constant treatment effect (constant OR)
implies that outcome risk in the treatment arm is a straight line parallel to
the first diagonal on the *log-odds* scale, with distance equal to $\log(\text{OR})$. 
We assessed the effect of stronger and absent relative treatment effects
($\text{OR}=0.5$ or $\text{OR}=1$). We also relaxed the assumption that the
line should be parallel to the diagonal, considering moderate and stronger
linear deviations. Finally, we dropped the assumption of linearity allowing for
quadratic deviations (Figure \@ref(fig:fig1)).

```{r fig1, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width='50%'}
knitr::include_graphics(here::here("figures/deviationsManuscript.png"))
knitr::include_graphics(here::here("figures/deviationsAbsoluteManuscript.png"))
```

@@

## Real data

>>>>

A true logistic regression model with a constant treatment effect (constant OR)
implies that outcome risk in the treatment arm is a straight line parallel to
the first diagonal on the *log-odds* scale, with distance equal to $\log(\text{OR})$. 
We assessed the effect of stronger and absent relative treatment effects
($\text{OR}=0.5$ or $\text{OR}=1$). We also relaxed the assumption that the
line should be parallel to the diagonal, considering moderate and stronger
linear deviations. Finally, we dropped the assumption of linearity allowing for
quadratic deviations.

@@

## Real data
```{r gusto, echo=FALSE, fig.cap="Caption", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/gusto.png"))
```
